Exploiting the Social Graph: Increasing Engagement in Collaborative Interactive Evolution

### 2017-01-27 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
First draft of conclusions
@JJ please help with conclusions, I added two paragraphs please check
them. Also now we are at 9 pages.

In all these systems, the interactive process is captured by the
system and no special attention is lent to the process of capturing
and engaging users themselves. In some cases, the genetic lineage of each
phenotypes is presented in a graphical interface 
where users can visualize the relationships between them, and evolutionary operators used in
their creation; they also display information regarding users and
their collaborations.  Common control panels  show, for instance,  
interesting phenotypes ordered by categories, number of votes, and
best of the week among others. In a recent work by 
Wagy \& Bongard \cite{wagy2014collective} user interaction is needed for evaluating the fitness and developing
new designs of robot locomotion. Collaboration is encouraged by gamifying the system 
using the maximum distance indicator to inspire the user to try and Ä'úbeat'Äù previous designs.

@@

\subsubsection{ Base deployment}
After a week of the announcement the total number of volunteers for this experiment was 53 registered users. 
The total number of nodes generated in the graph was 595, with a total of 2220 relationships. In this
experiment a total of 500 new phenotypes where generated. The total number of evaluated
phenotypes for each volunteer is presented in figure
\ref{fig:top-ranked-participation} in blue. Users are ranked by
the number of phenotypes they rated, in the \emph{x} axis is the rank, and in the \emph{y} axis 
the number of phenotypes evaluated using a logarithmic scale.   % Ranked by... - JJ

@@

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/user_known_2.png}
    \caption{User network view of the Base deployment}
    \label{fig:B-network}
\end{figure}
\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/user_known_3.png}
    \caption{User network view of the Graph Gamification deployment}
    \label{fig:GG-network}
\end{figure}
\begin{figure*}[!t]
    \centering
        \includegraphics[width=5.5in]{img/comparison.png}
    \caption{Users are ranked by
		the number of phenotypes they rated, in the \emph{x} axis is the rank, and in the \emph{y} axis 
		the number of phenotypes evaluated using a logarithmic scale. } % Explain a little more and label axes. The
                         % three lines have the same label,
                         % "participation". Not too clear - JJ
                         % TO DO -Mario
    \label{fig:top-ranked-participation}
\end{figure*}

@@

@@

>>>>

In all these systems, the interactive process is captured by the
system and no special attention is lent to the process of capturing
and engaging users themselves. In some cases, the genetic lineage of each
phenotypes is presented in a graphical interface 
where users can visualize the relationships between them, and evolutionary operators used in
their creation; they also display information regarding users and
their collaborations.  Common control panels  show, for instance,  
interesting phenotypes ordered by categories, number of votes, and
best of the week among others. In a recent work by 
Wagy \& Bongard \cite{wagy2014collective} user interaction is needed for evaluating the fitness and developing
new designs of robot locomotion. Collaboration is encouraged by gamifying the system 
using the maximum distance indicator to inspire the user to try and €'œbeat'€ previous designs.

@@

\subsubsection{ Base deployment}
After a week of the announcement the total number of volunteers for this experiment was 53 registered users. 
The total number of nodes generated in the graph was 595, with a total of 2220 relationships. In this
experiment a total of 500 new phenotypes where generated. The total number of evaluated
phenotypes for each volunteer is presented in figure
\ref{fig:top-ranked-participation} in blue. Users are ranked by
the number of phenotypes they rated, in the \emph{x} axis is the rank, and in the \emph{y} axis 
the number of phenotypes evaluated using a logarithmic scale.   % Ranked by... - JJ
% Done - Mario

@@

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/user_known_2.png}
    \caption{User network view of the Base deployment}
    \label{fig:B-network}
\end{figure}
\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/user_known_3.png}
    \caption{User network view of the Graph Gamification deployment}
    \label{fig:GG-network}
\end{figure}
\begin{figure*}[!t]
    \centering
        \includegraphics[width=5.5in]{img/comparison.png}
    \caption{Users are ranked by
		the number of phenotypes they rated, in the \emph{x} axis is the rank, and in the \emph{y} axis 
		the number of phenotypes evaluated using a logarithmic scale. } % Explain a little more and label axes. The
                         % three lines have the same label,
                         % "participation". Not too clear - JJ
                         % Done - Mario
    \label{fig:top-ranked-participation}
\end{figure*}

@@

Collaborative and volunteer based IEC systems involve the dynamic 
interaction of many entities and artifacts. Employing a multi-model approach
can benefit researchers to understand and visualize this kind of systems better.
In this paper a graph model was proposed as a complement to current models to
improve the visualization of different experiments. Further more, the same graph enabled
the implementation of a gamification technique to improve engagement in
a case stady.

@@

Another line of work would be to study the negative effects of using 
gamification techniques to improve engagment, like cheating or competition.
Finally, the refinement of the proposed Human-Centered frameworkwill need
more case studies and further multi-disciplinary research.
